---
title: "MSDS597_Assignment07"
author: "Linfeng He"
date: "11/6/2016"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(stringr)
```

## Maternal Mortality Data by country 
```{r }
mortality <- read_csv("data.csv")
mortality$`Maternal mortality ratio (per 100 000 live births)`  <- 
  mortality$`Maternal mortality ratio (per 100 000 live births)` %>%
  str_replace_all(., " ", "") %>%
  str_extract_all(., '\\[[0-9]+\\-[0-9]+\\]')
  
mortality$'Maternal mortality ratio lower_bound' <- 
  str_extract(mortality$`Maternal mortality ratio (per 100 000 live births)`, '[0-9]+') %>%
  as.numeric()

mortality$'Maternal mortality ratio upper_bound' <- 
    str_extract(mortality$`Maternal mortality ratio (per 100 000 live births)`, '\\-[0-9]+') %>%
    str_replace(., "-","") %>%
    as.numeric()

mortality$Year <-
    mortality$Year %>%
    str_replace_all(., '[0-9]+-',"") %>%
    as.numeric()
```

## The Gross National Income data 
```{r}
gni <- read_csv("GNI per capita.csv")
colnames(gni) <- gni[1,]
gni <- subset(gni[2:184,])
gni <- gather(gni, `2013`:`1990`, key = "year", value = "Gross national income per capital") 
gni$year <- as.numeric(gni$year)

gni$`Gross national income per capital` <-
    gni$`Gross national income per capital` %>%
    str_replace_all(., " ", "") %>%
    as.numeric()
```

### Merge the two files by country and year, retaining only rows for which you have per capita income *and* either maternal mortality *or* percentage attended births
```{r}
Countries <- inner_join(gni, mortality, c("Country"="Country","year" = "Year")) %>%
    filter(., !is.na(`Gross national income per capital`))
```

### Make a two polished  and informative graphs, one relating income to maternal mortality and the other relating income to percentage attended births
```{r}
ggplot(data = subset(Countries, year == "1990"), aes(`Gross national income per capital`)) +
  geom_point(alpha = 0.5, aes(y = `Maternal mortality ratio lower_bound`), colour = "blue") + 
  geom_point(alpha = 0.5, aes(y= `Maternal mortality ratio upper_bound` ), colour = "red")

ggplot(data = subset(Countries, year == "2000"), aes(`Gross national income per capital`)) +
  geom_point(alpha = 0.5, aes(y = `Maternal mortality ratio lower_bound`), colour = "blue") +
  geom_point(alpha = 0.5, aes(y= `Maternal mortality ratio upper_bound` ), colour = "green")


```
